Insert the article title here

### 2020-07-24 tex/background.tex
more on pygbe-lspr

Our research group has been developing PyGBe---pronounced \emph{pigb\={e}}---for several years. 
It was first written for biomolecular-electrostatics calculations using a continuum model of proteins in water or an ionic solution. 
The solution method applies a boundary integral approximation of the governing Poisson-Boltzmann or Poisson equations, to obtain electrostatic field and potential on the molecular surface. 
In the implicit-solvent model, this information is used to compute the quantity of interest: solvation energy, which is diagnostic for questions of protein binding affinity, protein-surface interactions, and others. 
PyGBe uses a fast-summation algorithm via a Barnes-Hut treecode \cite{BarnesHut1986}, and accelerates the computationally intensive parts of the code on NVIDIA GPU hardware using CUDA kernels in the treecode, interfacing with PyCUDA \cite{klockner2012pycuda}. 
Other portions of the code are written in C$++$, wrapped using \texttt{swig}, to extract more performance \cite{CooperETal2016}.

@@

In the last years polar dielectrics, like Silicon Carbide (SiC), have caught the attention as an alternative to plasmonic metals, due to their low optical losses in in the
mid to long wave infrared. Nanostructures of these materials show figure of merits that are not possible using plasmonic metals. This effect is due to the properties 
of the dielectric in the mid/long infrared region, where the real part has a negative value and the imaginary part is very small. This dielectric behavior is similar to the one 
be observed in metals like silver in the blue part of the wavelength spectrum. 
In plasmonics, when we illuminate a small particle made of metallic materials we will observe that certain wavelengths will excite a surface plasmon, which is the result of 
the oscillation of free electrons. The main difference with polar dielectrics like SiC is that for this material, is that the frequency of the incoming light matches instead the
resonance frequency of the Si and C sublattices \cite{caldwell2015,rockstuhl2005}. This excitation leads to a strong extinction cross section at the resonance wavelength, and an 
enhanced near field amplitude. These behavior can be model  with the same approached used for Localized surface plasmon resonance, and when the wavelength is bigger than the size
of the nanoparticle, we can still applied the electrostatic approach implemented in \pygbe \cite{ClementiETal2017, ClementiETal2019}.

>>>>

Our research group has been developing PyGBe---pronounced \emph{pigb\={e}}---for several years. 
It was first written for biomolecular-electrostatics calculations using a continuum model of proteins in water or an ionic solvent. 
The computational model applies a boundary integral form of the governing Poisson-Boltzmann and Poisson equations, to obtain the electrostatic field and potential on the molecular surface. 
In the implicit-solvent model, this information is used to compute the quantity of interest: solvation energy, which is diagnostic for questions of protein binding affinity, protein-surface interactions, and others. 
Biomolecules are modeled as dielectric cavities inside an infinite continuum solvent, and the partial differential equations are solved via a boundary element method, leading to a dense linear system of equations. 
PyGBe uses a fast-summation algorithm via a Barnes-Hut treecode \cite{BarnesHut1986}, and accelerates the computationally intensive parts of the code on Nvidia GPU hardware using CUDA kernels in the treecode, interfacing with PyCUDA \cite{klockner2012pycuda}. 
Other portions of the code are written in C$++$, wrapped using \texttt{swig}, to extract more performance \cite{CooperETal2016}. 
These features allow PyGBe to handle problems with half a million boundary elements or more.

In more recent work, we expanded the capabilities of PyGBE to applications of computational nanoplasmonics for biosensing \cite{ClementiETal2019}. 
Applying the long-wavelength limit, one can model the phenomenon of localized surface plasmon resonance (LSPR) via electrostatics, instead of the full Maxwell equations. 
This phenomenon is harnessed in nanosensors for detecting with high sensitivity the presence of biomolecules through shifts in resonance frequency. 
In LSPR, an electromagnetic wave excites the free electrons on the surface of a metallic nanoparticle. 
The name given to these electron-cloud vibrations is plasmons. 
In this setting, they resonate with the incoming field, and the energy is either absorbed by the nanoparticle or scattered in all directions, causing what's called extinction.
Since the resonance frequency depends on the dielectric environment, the change produced by a biomolecule approaching the metallic nanoparticle results in a frequency shift, and a means of detecting its presence.
The electrostatic approximation allows using the methods implemented in PyGBe, after substantial code development to permit using complex-valued permittivities, and to incorporate an external electric field into the model. 
These changes included re-writing the Krylov iterative solver to work with complex numbers, and splitting the treecode evaluation into real and imaginary parts. 
New functions were added to read from configuration files the data describing the electric field, to compute the dipole moment, and to compute the final quantity of interest: extinction cross-section. 
We reported a major new release of the software in 2017 \cite{ClementiETal2017}.

@@

In the last years polar dielectrics, like Silicon Carbide (SiC), have caught the attention as an alternative to plasmonic metals, due to their low optical losses in in the
mid to long wave infrared. Nanostructures of these materials show figure of merits that exceed that are not possible using plasmonic metals. This effect is due to the properties 
of the dielectric in the mid/long infrared region, where the real part has a negative value and the imaginary part is very small. This dielectric behavior is similar to the one 
be observed in metals like silver in the blue part of the wavelength spectrum. 
In plasmonics, when we illuminate a small particle made of metallic materials we will observe that certain wavelengths will excite a surface plasmon, which is the result of 
the oscillation of free electrons. The main difference with polar dielectrics like SiC is that for this material, is that the frequency of the incoming light matches instead the
resonance frequency of the Si and C sublattices \cite{caldwell2015,rockstuhl2005}. This excitation leads to a strong extinction cross section at the resonance wavelength, and an 
enhanced near field amplitude. These behavior can be model  with the same approached used for Localized surface plasmon resonance, and when the wavelength is bigger than the size
of the nanoparticle, we can still applied the electrostatic approach implemented in \pygbe \cite{ClementiETal2017, ClementiETal2019}.
